06-assessing_lime_explanations

### 2019-02-25 journals/06-assessing_lime_explanations/06-assessing_lime_explanations.Rmd

```{r}
# Load libraries
library(gretchenalbrecht)
library(tidyverse)

@@

>>>>

```{r}
# Load libraries
library(gretchenalbrecht)
library(seriation)
library(tidyverse)

@@

Now I am trying to use the function `seriate` from the seriation package to order the cases in the plots. However, something is going wrong. It ends up adding a bunch of NAs to the dataframe after I order the cases. I haven't figured out what is wrong yet.

```{r fig.height = 8, fig.width = 8, eval = FALSE}
order <- chosen_features %>% 
  filter(set == "Set 1", bin_situation == "samesource tree") %>%
  arrange(set, case) %>%
  select(case, nbins, first) %>%
  spread(key = nbins, value = first) %>%
  select(-case) %>%
  cluster::daisy() %>%
  seriate(method = "MDS") %>%
  get_order()

chosen_features %>% 
  filter(set == "Set 1") %>%
  mutate(case = factor(case)) %>%
  ggplot(aes(x = situation, y = case, fill = first)) + 
  geom_tile() + 
  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")

set1 <- chosen_features %>% 
  filter(set == "Set 1") %>%
  mutate(case = factor(case))

set12 <- chosen_features %>%
  filter(set == "Set 1") %>%
  mutate(case = factor(case, levels = order))

order == 272
unique(set1$case)
unique(set12$case)

sum(is.na(set1$case))
sum(is.na(set12$case))

data.frame(set1$case, set12$case) %>% View()

chosen_features %>%
  filter(set == "Set 1") %>%
  mutate(case = factor(case, levels = order)) %>%
  View()

  ggplot(aes(x = situation, y = case, fill = first)) + 
  geom_tile() + 
  facet_grid(set + samesource ~ bin_situation, scales = "free", space = "free_y") + 
  theme_bw() + 
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) + 
  scale_fill_gretchenalbrecht(palette = "last_rays", discrete = TRUE) + 
  labs(x = "Bin Type", y = "", fill = "Feature", title = "First Feature")
```
